Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2017-02-15 src/appendix.tex
fix some refs

\section{Figures}
\label{sec:figures}

\begin{figure}[h]
\centering
\input{fig-submodular}
\caption[]{%
We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
redistributed over \subref{sub:s} and \subref{sub:s} 
%\todo{write explanation}
}
\label{fig:sub}
\end{figure}

>>>>

\section{Figures}
%\label{sec:figures}

\begin{figure}[h]
\centering
\input{fig-submodular}
\caption[]{%
Given the two solutions on the left, 
\subref{sub:cup} and \subref{sub:cap}, we
can construct the two solutions on the right side,
\subref{sub:s} and \subref{sub:t}, with equal total weight.
The edges of type 
\inlineedge{e1}, 
\inlineedge{e2}, 
\inlineedge{e3}, 
\inlineedge{e5}, 
\inlineedge{e6}
from the left side are ``naturally'' distributed over the two solutions on the
right side and the edges of type \inlineedge{e4} can be distrebuted between the
two solutions without violating the capacity constraints.
}
\label{fig:sub}
\end{figure}

### 2017-02-15 src/local.tex
fix some refs

\begin{algorithm}
\caption{\textbf{EdgeSwap}$(G,c,k)$}
\label{alg:local}
\begin{small}
\SetKw{True}{true}
\SetKw{False}{false}
%\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
%\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
\label{line:outerloop}
 	$done \leftarrow{}$ \True							\\
 	\ForAll{$M' \subseteq M : |M'| \leq k$}{
 		\ForAll{$A' \subseteq A \setminus M : |A'| = |M'| + 1$}{
			\If{$M \setminus M' \cup A'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup A'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}
\end{small}
\end{algorithm}

@@

\begin{figure}[t]
%
\begin{subfigure}[t]{.4\linewidth}
\caption{\label{subfloat:graph}}
\input{fig-sub-graph}
\end{subfigure}
%
\hfill
%
\begin{subfigure}[t]{.4\linewidth}
\caption{\label{subfloat:conflict}}
\input{fig-sub-conflict}
\end{subfigure}
%
\caption[]{
\subref{subfloat:graph} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.
The optimal stars are outlined.  
\subref{subfloat:conflict}
The star graph, each vertex corresponded to a star in the original graph. 
The upper left vertex corresponds to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\label{fig:conflict}
\end{figure}

>>>>

\begin{algorithm}
\caption{\textbf{EdgeSwap}$(G,c,k)$}
\label{alg:local}
\begin{small}
\SetKw{True}{true}
\SetKw{False}{false}
%\KwIn{$G = (V, A)$, $c : V \rightarrow \N$, $k$}
%\KwOut{$M$}
$M \leftarrow \emptyset$								\\
\Repeat{done}{
 	$done \leftarrow{}$ \True							\\
 	\ForAll{$M' \subseteq M : |M'| \leq k$}{
 		\ForAll{$A' \subseteq A \setminus M : |A'| = |M'| + 1$}{
			\If{$M \setminus M' \cup A'$ is feasible}{
				$M \leftarrow{} M \setminus M' \cup A'$	\\
				$done \leftarrow{}$ \False				\\
			}
		}
 	}
}
\Return{$M$}
\end{small}
\end{algorithm}

@@

\begin{figure}[t]
\centering
%
\begin{subfigure}[t]{.45\linewidth}
\centering
\caption{
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.
The optimal stars are outlined.  
}
\input{fig-sub-graph}
\end{subfigure}
%
\hfill
%
\begin{subfigure}[t]{.53\linewidth}
\centering
\caption{
The star graph, each vertex corresponded to a star in the original graph. 
The upper left vertex corresponds to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\input{fig-sub-conflict}
\end{subfigure}
%
\caption{A \emph{Star Graph}}
\label{fig:conflict}
\end{figure}
